### 2017-03-21 main.tex
Wording.

We found these parameters to work well across a variety of target
syllables, but various other parameter sets yield results similar to
those presented here.  Some of the parameters trade off detection
accuracy or temporal precision vs.~training time. For example,
decreasing the frame interval generally decreases both latency and
jitter, but also increases training time. Sometimes the effects are
syllable-specific: for example, using a 30-ms time window rather than
50 ms speeds training while usually having a minimal effect on
detector performance, but occasionally a syllable will be seen for
which extending the window to 80 ms is very helpful.

@@

\begin{table}
 \begin{tabular}{c|ccc}
    Bird & Test songs = Test non-songs & Target time (ms) \\ \hline
    lny64 & 1818 & 150:50:400 \\
    lny46 & 1000 & 195 \\
    lny42 & 1245 & 380 \\
    lny4rb & 1000 & 250 \\
    lr12 & 2000 & 180 \\
    lr13 & 2000 & 300 \\
    lr28 & 3000 & 140 \\
    lr77 & 2000 & 320
  \end{tabular}
  \caption{For each bird, detectors were trained for the specified
    timepoints, using 1000 songs and 1000 non-song samples of the same
    length. The test set consisted of the remaining songs and an
    equal number of non-songs.}
  \label{table:datasizes}
\end{table}

Data consisted of extracted, aligned songs, and additional song-length
samples of non-song (cage noise, calls, other birds' song). These were
divided into training and test sets. For all birds, we used 1000 songs
and 1000 non-song samples for training. The test set consisted of the remaining songs and an equal number of non-songs. Table~\ref{table:datasizes}
lists the test dataset sizes and target detection points. For lny64,
we arbitrarily chose six linearly spaced target times. For each of the
other birds, we eyeballed one promising-looking detection point.

>>>>

We found these parameters to work well across a variety of target
syllables, but various other parameter sets yield results similar to
those presented here.  Some of the parameters trade off detection
accuracy or temporal precision vs.~training time. For example,
decreasing the frame interval generally decreases both latency and
jitter, but also increases training time. Sometimes the effects are
syllable-specific: for example, using a 30-ms time window rather than
50 ms speeds training while usually having a minimal effect on
detector performance (as is the case, for example, for all of the
detection points for lny64), but occasionally a syllable will be seen
for which extending the window to 80 ms is very helpful.

@@

\begin{table}
 \begin{tabular}{c|ccc}
    Bird & Test songs & Test non-songs & Target time (ms) \\ \hline
    lny64 & 1818 & 10545 & 150:50:400 \\
    lny46 & 1000 & 1000 & 195 \\
    lny42 & 1245 & 1223 & 380 \\
    lny4rb & 1000 & 1000 & 250 \\
    lr12 & 2000 & 2008 & 180 \\
    lr13 & 2000 & 2001 & 300 \\
    lr28 & 3000 & 3014 & 140 \\
    lr77 & 2000 & 2008 & 320
  \end{tabular}
  \caption{For each bird, detectors were trained for the specified
    timepoints, using 1000 songs and 1000 non-song samples of the same
    length. The rest of the audio samples---shown here---were used to
    test the learned detectors.}
  \label{table:datasizes}
\end{table}

Data consisted of extracted, aligned songs, and additional song-length
samples of non-song (cage noise, calls, other birds' song). These were
divided into training and test sets. For all birds, we used 1000 songs
and 1000 non-song samples for training. Table~\ref{table:datasizes}
lists the test dataset sizes and target detection points. For lny64,
we arbitrarily chose six linearly spaced target times. For each of the
other birds, we eyeballed one promising-looking detection point.
